\sysfull

### 2018-04-17 paper/background.tex
shortened and changed bg text

\textbf{Incorrectly Sized Tasks.} Compiler-inserted checkpoints or programmer-defined tasks can both be incorrect or inefficient.
If the code between checkpoints or the task (for brevity, we will refer to both as ''tasks'' in this section) consumes {\em more} 
energy than the device can buffer, the task will never complete 
using buffered energy {\em preventing forward progress}, making the system incorrect. 
%
If the task consumes far {\em less} energy than a device can buffer, the system may operate {\em inefficiently},
checkpointing or transitioning between tasks too often than needed. 
%
Avoiding excessively costly, non-terminating tasks and short, high-overhead tasks is challenging both to the
programmer and the compiler, since estimating the exact energy use of an arbitrary code is complicated.
Consequently, existing systems either risks non-termination to achieve high performance, or 
use conservatively small tasks that result in poor performance. 
When {\em porting} apps from one device to another, the problem gets much worse.
An excessively costly task on a device with a small energy buffer may be a relatively short task on a device with a larger buffer, and vice versa. 
Buffer sizes from prior work on intermittently-powered computing hardware vary widely from 20\,$\mu $F~\cite{rodriguez_tbcs_2015} to 0.1\,F~\cite{moo},
exemplifying the problem.
%
As a solution, \sys's execution model is based on {\em task coalescing} and {\em task downscaling}.  
Coalescing dynamically merges multiple tasks based on execution behavior to amortize the overhead between tasks if tasks are small.
Downscaling breaks up a single task into multiple subtasks that commit individually to avoid executing a single task that is too 
large to complete using the device's buffered energy.  Section~\ref{sec:task_adaptation} describes \sys's adaptive coalescing and 
downscaling mechanisms in detail. The main enabler for \sys's adaptation is its novel \emph{memory virtualization} mechanism, 
which is described in Section~\ref{sec:memory_virtulaization}.
%When a task and its successor both complete, the two tasks were interleaved by a task boundary that preserves progress and state (i.e., checkpoint or commit). However, absent a power failure, the work to preserve state was {\em unnecessary}, incurring overhead on the tasks' executions. Avoiding excessively costly, non-terminating tasks and short, high-overhead tasks is a programming challenge, given fixed hardware (no support from dedicated circuitry to measure the state of energy buffer) with a fixed energy buffering capacity. Buffer sizes from prior work on intermittently-powered computing hardware vary widely from 20\,$\mu $F~\cite{rodriguez_tbcs_2015} to 0.1\,F~\cite{moo}. Sizing tasks complicates {\em porting} code from one device to another. An excessively costly task on a device with a small energy buffer may be a relatively short task on a device with a larger buffer. The key problem is that using existing systems, by defining tasks statically for a fixed energy buffer, the programmer either risks non-termination or poor performance due to high overhead. \sys's execution model based on {\em task coalescing} and {\em task downscaling}.  Coalescing dynamically merges multiple tasks based on execution behavior to amortize the cost of committing each task separately. Downscaling breaks up a single task into multiple subtasks that commit individually to avoid executing a single task that is too large to complete using the device's buffered energy.  Section~\ref{sec:task_adaptation}describes \sys's adaptive coalescing and downscaling mechanisms in detail. The main enabler for \sys's adaptation is its novel \emph{memory virtualization} mechanism, which is described in Section~\ref{sec:memory_virtulaization}.

>>>>

\textbf{Incorrectly Sized Tasks.} Compiler-inserted checkpoints or programmer-defined tasks can both be incorrect or inefficient.
If the code between checkpoints or the task (for brevity, we will refer to both as ''tasks'' in this section) consumes {\em more} 
energy than the device can buffer, the task will never complete 
using buffered energy {\em preventing forward progress}, making the system incorrect. 
%
If the task consumes far {\em less} energy than a device can buffer, the system may operate {\em inefficiently},
checkpointing or transitioning between tasks too often than needed. 
%
Avoiding excessively costly, non-terminating tasks and short, high-overhead tasks is challenging both to the
programmer and the compiler, since estimating the exact energy use of an arbitrary code is complicated.
When {\em porting} apps from one device to another, the problem gets much worse because
an excessively costly task on one device may be a relatively short task on a device with a larger buffer, and vice versa. 
Buffer sizes of different platforms vary widely from 20\,$\mu $F~\cite{rodriguez_tbcs_2015} to 0.1\,F~\cite{moo},
complicating the problem.
%
As a solution, \sys's execution model presents {\em task coalescing}, which merges multiple tasks to amortize the overhead
when tasks are too small, and {\em task downscaling}, which breaks up a task when the task is too large. 
%When a task and its successor both complete, the two tasks were interleaved by a task boundary that preserves progress and state (i.e., checkpoint or commit). However, absent a power failure, the work to preserve state was {\em unnecessary}, incurring overhead on the tasks' executions. Avoiding excessively costly, non-terminating tasks and short, high-overhead tasks is a programming challenge, given fixed hardware (no support from dedicated circuitry to measure the state of energy buffer) with a fixed energy buffering capacity. Buffer sizes from prior work on intermittently-powered computing hardware vary widely from 20\,$\mu $F~\cite{rodriguez_tbcs_2015} to 0.1\,F~\cite{moo}. Sizing tasks complicates {\em porting} code from one device to another. An excessively costly task on a device with a small energy buffer may be a relatively short task on a device with a larger buffer. The key problem is that using existing systems, by defining tasks statically for a fixed energy buffer, the programmer either risks non-termination or poor performance due to high overhead. \sys's execution model based on {\em task coalescing} and {\em task downscaling}.  Coalescing dynamically merges multiple tasks based on execution behavior to amortize the cost of committing each task separately. Downscaling breaks up a single task into multiple subtasks that commit individually to avoid executing a single task that is too large to complete using the device's buffered energy.  Section~\ref{sec:task_adaptation}describes \sys's adaptive coalescing and downscaling mechanisms in detail. The main enabler for \sys's adaptation is its novel \emph{memory virtualization} mechanism, which is described in Section~\ref{sec:memory_virtulaization}.
